3D MAGNETIC MODELLING FOR ELIPSOIDS

### 2017-01-11 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Update metodologia

\begin{abstract}
In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by triaxial and prolate elipsoidal sources. Such approach provide analytical results for anisotropy of magnetic susceptibility as well as for self-demagnetization effects, which can be easily adapted for distinctive geologic structures - hence being an useful tool for educational (e.g., potential methods and rock magnetism) and applied geophysics (e.g., characterization of high magnetic susceptibility, mineralized bodies) purposes. Numerical tests by means of a Python code (currently under development) allowed us to compared the effects of different geometries (ellipsoidal sources, spheres, dipole lines and elliptic cylinders), which were used to validate our computational implementation. This code will be freely available to the scientific community by the end of the year.
\end{abstract}

@@

The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, that includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface. This difference can be written as:
\begin{equation} \label{eq:1}
\Delta T^0_i = ||T_i|| - ||F_i||,
\end{equation}
where $\Delta T^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm. The total-field vector $T_i$ is:
\begin{equation}\label{eq:2}
T_i = F_i + B_i,
\end{equation}
and $B_i$ is the total induced magnetization vector produced by all sources of anomalous susceptibility distribuition.
Considering $F_i$ a constant vector, $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
\begin{equation}\label{eq:3}
||T_i|| \approx ||F_0 + B_i|| \approx ||F_0|| + F^T B_i
\end{equation}
where $T$ indicates transposition and
\begin{equation}\label{eq:4}
\hat{F} = \dfrac{F_o}{||F_0||}
\end{equation}

is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the Eq.(\ref{eq:1}) of total-field anomaly to:
\begin{equation}\label{eq:5}
\Delta T \approx \hat{F}^T \bar{B}_i, \quad i=1,...,NF
\end{equation}

The field now $\bar{B}_i$ is represented this way to show that is in the geographic coordinates. One of the main steps to calculate the magnetic field of an ellipsoid is to change this system of coordinates to the body coordinates with origin in the center of it. The conversion can be done through a matrix of rotation $\bar{\bar{V}}$ that differs with the geometric type of ellipsoid, so the formulas will be shown later, separately for each one. But, in a general way, the conversion is:
\begin{equation}\label{eq:5}
\bar{r}_i = \bar{\bar{V}} \tilde{r}_i + \bar{r}_c,
\end{equation}

The vector $\bar{r}_i$ has the positions $x,y,z$ in the geographic coordinates, $\bar{r}_i$ has the positions $x1,x2,x3$ in the body coordinates and $\bar{r}_c$ is the position of the center of the body in the geographic coordinates.

The same way the matrix of conversion can be used to change the magnetic field calculate in the body coordinates, back to the geopraphic, where is more useful to us:
\begin{equation}\label{eq:5}
\bar{B}_i = \bar{\bar{V}} \tilde{B}_i
\end{equation}

\subsection{The Forward model of a sphere}

\subsection{The Forward model of a triaxial elipsoid}
The implementation of the forward problem of a triaxial elipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its origin is the center of this elipsoidal body.

This new coordinate system ($x_1,x_2,x_3$) is defined by the unit vectors $\hat{v}_h (h=1,2,3)$ with the respect with the geographic axis $x$, $y$ e $z$:
\begin{equation}
\textbf{v}_1 = (l_1,m_1,n_1) = (-\cos\alpha \cos\delta, -\sin\alpha \cos\delta, -\sin\delta)
\end{equation}

\begin{equation}
\begin{split}
\textbf{v}_2 = (l_2,m_2,n_2) = (\cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma,\\ \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\gamma \cos\delta)
\end{split}
\end{equation}

\begin{equation}
\begin{split}
\textbf{v}_3 = (l_3,m_3,n_3) = (\sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta,\\ -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta, \sin\gamma \cos\delta)
\end{split}
\end{equation}

The angles referring to the unit vectors are determined by the orientations of the elipsoid's semi-axis. The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$. While $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane. Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the elipsoid's center with the geographic plane.

Thus, the coordinates of the body's semi-axis are given by:

\begin{equation}
x_h = (x-xc)l_h + (y-yc)m_h + (z-zc)n_h \quad (h= 1,2,3)
\end{equation}

Where $x_c$, $y_c$ e $z_c$ are the coordinates of the elipsoid's center in the geographic system $x$, $y$ e $z$.

For an elipsoid of semi-axis $a > b > c$, the equation that defines your surface is:

\begin{equation} \label{eq:elipsoide}
\dfrac{x_1^2}{(a^2+s)} + \dfrac{x_2^2}{(b^2+s)} + \dfrac{x_3^2}{(c^2+s)} = 1
\end{equation}

The parameter $s$ controls the elipsoid form. When $s$ gets close to $\infty$ the equation \eqref{eq:elipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$. When $s = -c^2$, the last term of the elipsoid's equation is less than zero and it becomes the equation of a circle.

@@

This set of roots, called elipsoidal coordinates, correspond to the parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates. Their expressions are:

@@

The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:elipsoide}, where $s$ admits the value of $\lambda$.

@@

The desmagnetization factors are given by:

@@

The Earth's field vector, $F$, and the remanent magnetization ,$d$, also must be converted to the body's coordinates:

\begin{equation}
F_h = F(l \, l_h + m \, m_h + n \, n_h)
\end{equation}

\begin{equation}
(J_N)_h = J_N (l_N l_h + m_n m_h + n_N n_h)
\end{equation}

Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ e $l_N, m_N, n_N$ depends on their respective vectors of inclinations and declinations:
\begin{equation}
L_R,l,l_N = \cos(dec) \, \cos(inc)
\end{equation}

@@

\begin{equation}
\textbf{J}_R = K\textbf{F} + \textbf{J}_{NRM}
\end{equation}

@@

\begin{equation}
\textbf{J}_{Rc} = A^{-1} \textbf{J}_R
\end{equation}

@@

\begin{equation}
A = I + KN = \left[\begin{matrix} 
1+k_{11}N_1 \quad & k_{12}N_2 \quad & k_{13}N_3 \\\\
k_{21}N_1 \quad & 1+k_{22}N_2 \quad & k_{23}N_3 \\\\
k_{31}N_1 \quad & k_{23}N_2 \quad & 1+k_{33}N_3
\end{matrix}\right]
\end{equation}

This way, the components of the magnetic field produced by a triaxial elipsoid in the body's coordinates outside of it is:

\begin{equation} \label{eq:campo_e}
\Delta B_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
\end{equation}

\begin{equation}
\Delta B_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
\end{equation}

\begin{equation}
\Delta B_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
\end{equation}

@@

Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's eliptical integrals. While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an elipsoid. This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:

@@

Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient. Thus, the magnetic field generated by the elipsoid is:

\begin{equation}\label{eq:campoGeo}
b_i^j = 2\pi a_j b_j c_j \times [M_i^j - D_i^j] \times J^j \quad j=1,...,L
\end{equation}

@@

\begin{equation}
M_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
\left[\begin{matrix} 
\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
\end{matrix}\right]_{3 \times 3}
\end{equation}

\begin{equation}
D_i^j =
\left[\begin{matrix} 
A(\lambda) & 0 & 0 \\
0 & B(\lambda) & 0 \\
0 & 0 & C(\lambda)
\end{matrix}\right]
\end{equation}

For $j = 1,...,L$, the number of elipsoids been modeled and $i = 1,...,N$  for the $i$th element of the calculated field. The total magnetic field then is:

\begin{equation}\label{eq:campoGeoNL}
B_i = \sum_{j=1}^{L} b_i^j, \quad i=1,...,N
\end{equation}

We must remember that every calculation so far was done using the body's coordinates, however the notation in equation \eqref{eq:campoGeo} the magnetic field is already in geographics coordinates. To calculate each component of the magnetic field's vector back:

\begin{equation}
\Delta B_x = \Delta B_1l_1 + \Delta B_2l_2 + \Delta B_3l_3
\end{equation}

\begin{equation}
\Delta B_y = \Delta B_1m_1 + \Delta B_2m_2 + \Delta B_3m_3
\end{equation}

\begin{equation}
\Delta B_z = \Delta B_1n_1 + \Delta B_2n_2 + \Delta B_3n_3
\end{equation}

>>>>

\begin{abstract}
In this work we will present results from a numerical modeling of the magnetic field and total field anomaly, represented by triaxial and prolate ellipsoidal sources. Such approach provide analytical results for anisotropy of magnetic susceptibility as well as for self-demagnetization effects, which can be easily adapted for distinctive geologic structures - hence being an useful tool for educational (e.g., potential methods and rock magnetism) and applied geophysics (e.g., characterization of high magnetic susceptibility, mineralized bodies) purposes. Numerical tests by means of a Python code (currently under development) allowed us to compared the effects of different geometries (ellipsoidal sources, spheres, dipole lines and elliptic cylinders), which were used to validate our computational implementation. This code will be freely available to the scientific community by the end of the year.
\end{abstract}

@@

The total-field anomaly can be described as a difference between the total field vector and the induced magnetization of the crust of the Earth, that includes any anomalous distribuition of magnetization that can occur by magnetizied bodies in subsurface. This difference can be written as:
\begin{equation} \label{eq:1}
\Delta \textbf{T}^0_i = ||\textbf{T}_i|| - ||\textbf{F}_i||,
\end{equation}
where $\Delta \textbf{T}^0_i$ is the observed vector of total-field anomaly in the $i$-th position ($x_i$, $y_i$, $z_i$), $i = 1,...N$, $F_i$ is the geomagnetic field and $||.||$ is the Euclidian norm. The total-field vector $T_i$ is:
\begin{equation}\label{eq:2}
\textbf{T}_i = \textbf{F}_i + \textbf{B}_i,
\end{equation}
and $B_i$ is the total induced magnetization vector produced by all sources of anomalous susceptibility distribuition.
Considering $F_i$ a constant vector, $F_0$ for local ou regional scale, and that $||F_0|| \gg ||B_0||$, since, $B_i$ is a small pertubation of the magnetic field $F_i$, we can approximate the euclidian norm of the vector $T_i$ by a Taylor's expansion of first order:
\begin{equation}\label{eq:3}
||\textbf{T}_i|| \approx ||\textbf{F}_0 + \textbf{B}_i|| \approx ||\textbf{F}_0|| + \textbf{F}^T \textbf{B}_i
\end{equation}
where $T$ indicates transposition and
\begin{equation}\label{eq:4}
\textbf{F} = \dfrac{\textbf{F}_o}{||\textbf{F}_0||}
\end{equation}

is a unit vector that represents the gradient of the function $||T_i||$ in relation to the vector's components $T_i$. This way, we can approximate the Eq.(\ref{eq:1}) of total-field anomaly to:
\begin{equation}\label{eq:5}
\Delta T \approx \textbf{F}^T \textbf{B}_i, \quad i=1,...,NF
\end{equation}

The field now $\textbf{B}_i$ is represented this way to show that is in the geographic coordinates. One of the main steps to calculate the magnetic field of an ellipsoid is to change this system of coordinates to the body coordinates with origin in the center of it. The conversion can be done through a matrix of rotation $\textbf{V}$ that differs with the geometric type of ellipsoid, so the formulas will be shown later, separately for each one. But, in a general way, the conversion is:
\begin{equation}\label{eq:6}
\textbf{r}_i = \textbf{\textbf{V}} \tilde{\textbf{r}}_i + \textbf{r}_c,
\end{equation}

The vector $\textbf{r}_i$ has the positions $x,y,z$ in the geographic coordinates, $\tilde{\textbf{r}}_i$ has the positions $x1,x2,x3$ in the body coordinates and $\textbf{r}_c$ is the position of the center of the body in the geographic coordinates. The columns of $\textbf{\textbf{V}}$ are the eigenvectors that represents the directions cosines of the semi axes of the ellipsoid:
\begin{equation}
\textbf{\textbf{V}} =
\left[\begin{matrix} 
l_1 & l_2 & l_3 \\
m_1 & m_2 & m_3 \\
n_1 & n_2 & n_3
\end{matrix}\right] = 
\left[\begin{matrix} 
\textbf{v}_1 \\
\textbf{v}_2 \\
\textbf{v}_3
\end{matrix}\right]
\end{equation}

The equation of the surface of an ellipsoid can be written in a matrix form as:
\begin{equation}
(\textbf{r} - \textbf{r}_c)^T \textbf{A} (\textbf{r} - \textbf{r}_c) = 1,
\end{equation}

and $\textbf{\textbf{A}}$ is a 3X3 matrix formed by:
\begin{equation}
\textbf{\textbf{A}} = \textbf{\textbf{V}} 
\left[\begin{matrix} 
\dfrac{1}{a^2+s} & 0 & 0 \\
0 & \dfrac{1}{b^2+s} & 0 \\
0 & 0 & \dfrac{1}{c^2+s}
\end{matrix}\right]
\textbf{\textbf{V}}^T,
\end{equation}

The diagonal of the middle matrix, the eigenvalues that represents the reciprocals of the square of the semi-axes $a^{-2}$, $b^{-2}$ and $c^{-2}$.

For all types of ellipsoids the magnetic field can be written as:
\begin{equation}\label{eq:campoGeoNL}
\tilde{\textbf{B}}_i = \sum_{j=1}^{L} \tilde{\textbf{b}}_i^j, \quad i=1,...,N
\end{equation}

where $\textbf{b}_i^j$ is:
\begin{equation}\label{eq:campoGeo}
\tilde{\textbf{b}}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \tilde{\textbf{J}}^j \quad j=1,...,L
\end{equation}

The matrices $\textbf{M}_i^j$ and $\textbf{D}_i^j$ are different for each one, therefore they will be shown separately in the next sections.

The same way the matrix of conversion can be used to change the magnetic field $\tilde{\textbf{B}}_i$ calculated in the body coordinates, back to the geopraphic, where is more useful to us:
\begin{equation}\label{eq:7}
\textbf{B}_i = \textbf{V} \tilde{\textbf{B}}_i
\end{equation}

Leading to:
\begin{equation}
\Delta \textbf{B}_x = \Delta \tilde{\textbf{B}}_1l_1 + \Delta \tilde{\textbf{B}}_2l_2 + \Delta \tilde{\textbf{B}}_3l_3
\end{equation}
\begin{equation}
\Delta \textbf{B}_y = \Delta \tilde{\textbf{B}}_1m_1 + \Delta \tilde{\textbf{B}}_2m_2 + \Delta \tilde{\textbf{B}}_3m_3
\end{equation}
\begin{equation}
\Delta \textbf{B}_z = \Delta \tilde{\textbf{B}}_1n_1 + \Delta \tilde{\textbf{B}}_2n_2 + \Delta \tilde{\textbf{B}}_3n_3
\end{equation}

\subsection{The forward model of a triaxial ellipsoid}

The implementation of the forward problem of a triaxial ellipsoid's magnetic field (three semi-axis $a > b > c$) is done in a new coordinate system, where its origin is the center of this ellipsoidal body.

This new coordinate system ($x_1,x_2,x_3$) is defined by the unit vectors $\textbf{v}_h (h=1,2,3)$ with the respect with the geographic axis $x$, $y$ e $z$:
\begin{equation}
\textbf{v}_1 = (l_1,l_2,l_3) = (-\cos\alpha \cos\delta, \cos\alpha \cos\gamma \sin\delta + \sin\alpha \sin\gamma, \sin\alpha \cos\gamma - \cos\alpha \sin\gamma \sin\delta)
\end{equation}

\begin{equation}
\textbf{v}_2 = (m_1,m_2,m_3) = (-\sin\alpha \cos\delta, \sin\alpha \cos\gamma \sin\delta - \cos\alpha \sin\gamma, -\cos\alpha \cos\gamma - \sin\alpha \sin\gamma \sin\delta)
\end{equation}

\begin{equation}
\textbf{v}_3 = (n_1,n_2,n_3) = (-\sin\delta,-\cos\gamma \cos\delta, \sin\gamma \cos\delta)
\end{equation}

The angles referring to the unit vectors are determined by the orientations of the ellipsoid's semi-axis. The angle $\alpha$ is the azimuth of semi-major axe ($a$) plus 180$^{\circ}$. While $\delta$ is the inclination of semi-major axe ($a$) in relation to the geographic plane. Lastly, $\gamma$ is the angle between the semi-mid axe ($b$) and the vertical projection of the ellipsoid's center with the geographic plane.

Thus, the body's coordinates are given by:

\begin{equation} \label{eq:bodyco}
x_h = (x-xc)l_h + (y-yc)m_h + (z-zc)n_h \quad (h= 1,2,3)
\end{equation}

Where $x_c$, $y_c$ e $z_c$ are the coordinates of the ellipsoid's center in the geographic system $x$, $y$ e $z$.

For an ellipsoid of semi-axis $a > b > c$, the equation that defines your surface is:

\begin{equation} \label{eq:ellipsoide}
\dfrac{x_1^2}{(a^2+s)} + \dfrac{x_2^2}{(b^2+s)} + \dfrac{x_3^2}{(c^2+s)} = 1
\end{equation}

The parameter $s$ controls the ellipsoid form. When $s$ gets close to $\infty$ the equation \eqref{eq:ellipsoide} tends to the sphere equation of radius $r=\sqrt{\lambda}$. When $s = -c^2$, the last term of the ellipsoid's equation is less than zero and it becomes the equation of a circle.

@@

This set of roots, called ellipsoidal coordinates, correspond to the parameters of a point ($x_1,x_2,x_3$) which are under the intersection of three ortogonal surfaces related to the body coordinates. Their expressions are:

@@

The calculation of the largest root $\lambda$ of the equation \eqref{eq:cubica} is essential, since the magnetic field depends on the spatial derivatives of the equation \ref{eq:ellipsoide}, where $s$ admits the value of $\lambda$.

@@

The demagnetization factors are given by:

@@

The Earth's field vector, $F$, and the remanent magnetization ,$J_N$, also must be converted to the body's coordinates:

\begin{equation}
\textbf{F}_i = F(l \, l_i + m \, m_i + n \, n_i)
\end{equation}

\begin{equation}
(\textbf{J}_N)_i = J_N (l_N l_i + m_n m_i + n_N n_i)
\end{equation}

Note that $L_r, M_r, N_r$ ($r = 1,2,3$), $l,m,n$ and $l_N, m_N, n_N$ depends on their respective angles of inclinations and declinations:
\begin{equation}
L_R,l,l_N = \cos(dec) \, \cos(inc)
\end{equation}

@@

\begin{equation}
\textbf{J}_R = \textbf{K}\textbf{F} + \textbf{J}_{NRM}
\end{equation}

@@

\begin{equation}
\textbf{J}_{Rc} = \textbf{G}^{-1} \textbf{J}_R
\end{equation}

@@

\begin{equation}
\textbf{G} = I + KN = \left[\begin{matrix} 
1+k_{11}N_1 \quad & k_{12}N_2 \quad & k_{13}N_3 \\\\
k_{21}N_1 \quad & 1+k_{22}N_2 \quad & k_{23}N_3 \\\\
k_{31}N_1 \quad & k_{23}N_2 \quad & 1+k_{33}N_3
\end{matrix}\right]
\end{equation}

This way, the components of the magnetic field produced by a triaxial ellipsoid in the body's coordinates outside of it is:

\begin{equation} \label{eq:campo_e}
\Delta \textbf{B}_1 = f_1 \dfrac{\partial \lambda}{\partial x_1} - 2 \pi abc \, J_1 \, A(\lambda) 
\end{equation}

\begin{equation}
\Delta \textbf{B}_2 = f_1 \dfrac{\partial \lambda}{\partial x_2} - 2 \pi abc \, J_2 \, B(\lambda)
\end{equation}

\begin{equation}
\Delta \textbf{B}_3 = f_1 \dfrac{\partial \lambda}{\partial x_3} - 2 \pi abc \, J_3 \, C(\lambda)
\end{equation}

@@

Both $F(\theta^{'}, k)$ as $E(\theta^{'}, k)$ are again the first and second  noraml Legendre's eliptical integrals. While $A(\lambda), B(\lambda), C(\lambda)$ are analytic solutions of the integrals of the potential equation of an ellipsoid. This problem was solved by Dirichlet in 1839 \citep{clark1986magnetic} for the gravitational potential given by:

@@

Using the equations from \eqref{eq:campo_e} to \eqref{eq:integralC}, we can rearrange them in a matrix format that will be more computationally efficient. Thus, the magnetic field generated by the triaxial ellipsoid \eqref{eq:campoGeo} is:

\begin{equation}
\textbf{b}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \textbf{J}^j \quad j=1,...,L
\end{equation}

@@

\begin{equation}
\textbf{M}_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
\left[\begin{matrix} 
\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
\end{matrix}\right]_{3 \times 3}
\end{equation}

\begin{equation}
\textbf{D}_i^j =
\left[\begin{matrix} 
A(\lambda) & 0 & 0 \\
0 & B(\lambda) & 0 \\
0 & 0 & C(\lambda)
\end{matrix}\right]
\end{equation}

\subsection{The forward model of a prolate ellipsoid}

The same way that the triaxial ellipsoid, the magnetic field generated by a prolate ellipsoid ($a$ > $b$), must be calculated in the body's coordinate. In this case the matrix $\textbf{V}$ is composed by the same equations shown for the triaxial, but considering gamma equal to $0^o$ :
\begin{equation}
\textbf{v}_1 = (l_1,l_2,l_3) = (-\cos\alpha \cos\delta, \cos\alpha \sin\delta, \sin\alpha)
\end{equation}

\begin{equation}
\textbf{v}_2 = (m_1,m_2,m_3) = (-\sin\alpha \cos\delta, \sin\alpha \sin\delta, -\cos\alpha)
\end{equation}

\begin{equation}
\textbf{v}_3 = (n_1,n_2,n_3) = (-\sin\delta, -\cos\delta, 0)
\end{equation}

The coordinate transformation is the same as equation \eqref{eq:bodyco}.
The calculation of $\lambda$ is and its spatial derivatives are:
\begin{equation}
\lambda = \dfrac{r^2-a^2-b^2+ \Delta}{2},
\end{equation}

where:
\begin{equation}
r = \sqrt{x^2_1 + x^2_2 + x^2_3},
\end{equation}

and
\begin{equation}
\Delta = \sqrt{r^4 - (a^2-b^2)^2 -2(a^2-b^2)(x^2_1 - x^2_2 - x^2_3)},
\end{equation}

Hence its spatial derivatives are:
\begin{equation}
\dfrac{\partial \lambda}{\partial x_1} = x_1 \left(1 + \dfrac{r^2-a^2+b^2}{\Delta}\right)
\end{equation}

\begin{equation}
\dfrac{\partial \lambda}{\partial x_2} = x_2 \left(1 + \dfrac{r^2+a^2-b^2}{\Delta}\right)
\end{equation}

\begin{equation}
\dfrac{\partial \lambda}{\partial x_3} = x_3 \left(1 + \dfrac{r^2+a^2-b^2}{\Delta}\right)
\end{equation}

The demagnetization factor are:
\begin{equation}
N_1 = \dfrac{4\pi ab^2}{(a^2-b^2)^{3/2}} \left\{ \log_e \left[\left(\sqrt{\dfrac{a^2}{b^2}-1}\right) + \dfrac{a}{b}\right] - \sqrt{\left(1 - \dfrac{b^2}{a^2}\right)} \right\}
\end{equation}

\begin{equation}
N_2 = 2\pi - \dfrac{N_1}{2}
\end{equation}

The calculations of the susceptibility tensor $k$, Earth's field $\textbf{F}_i$, remanent magnetization vector $(\textbf{J}_N)_i$ and the resultant magnetization vector $\textbf{J}_{Rc}$ are the same as the triaxial ellipsoid.

The magnetic field generated by the prolate ellipsoid \eqref{eq:campoGeo} can also be written in a matrix form as:

\begin{equation}
\textbf{b}_i^j = 2\pi a_j b_j c_j \times [\textbf{M}_i^j - \textbf{D}_i^j] \times \textbf{J}^j \quad j=1,...,L
\end{equation}

\begin{equation}
\textbf{M}_i^j = \dfrac{1}{\sqrt{[(a^2+\lambda)(b^2+\lambda)(c^2+\lambda)]}}
\left[\begin{matrix} 
\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{c^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{c^2+\lambda}
\end{matrix}\right]_{3 \times 3}
\end{equation}

\begin{equation}
\textbf{D}_i^j =
\left[\begin{matrix} 
A(\lambda) & 0 & 0 \\
0 & B(\lambda) & 0 \\
0 & 0 & C(\lambda)
\end{matrix}\right]
\end{equation}

\subsection{The forward model of a oblate ellipsoid}
